Last glacial cycle glacier erosion potential in the Alps

### 2020-12-14 articles/erosion/alps-erosion.tex
Add Alps erosion paper tentative outline.
Add uncommited ideas from old spark prop draft.

% ----------------------------------------------------------------------
%\section{Introduction}
% ----------------------------------------------------------------------

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
%\subsection{Erosion}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

@@

%    \begin{figure}
%      \centerline{\includegraphics{alpero_glerosion}}
%      \caption{%
%          Modelled glacial erosion over the last glacial cycle.}
%      \label{fig:glerosion}
%    \end{figure}

>>>>

% ----------------------------------------------------------------------
\section{Introduction}
% ----------------------------------------------------------------------

    The glacial landscape of the Alps has fascinated generations of explorers,
    artists, mountaineers and scientists for centuries.

    In fact, the global obsession for the Alps has been so large that in
    English, a non-native language foreign to the Alps, the word “alpine” is
    now used to describe any glacially modified mountain landscape worldwide.

    Understanding the beauty of Alpine glacial landscape through the rigour of
    scientific research is yet another endeavour.

    While it has long been understood that glaciers leave a specific imprint on
    the landscape they lie on, observing and quantifying the long-term erosion
    and sedimentation processes has been a challenge. While some regions are
    specifically characterised by cirque glaciation (), or glacial scouring (),
    the European Alps present a variety of glacial landforms with a density
    seen in few other places on Earth.

    It is typically assumed that the degree of glacial modification is a proxy
    for the duration of past glacier cover. However glacier sliding velocities
    vary by several orders of magnitude, and erosion laws can be non-linear.
    Besides, cold-based glaciers have been shown to preserve landscape.

    Fig.~\ref{fig:photos} -- Alpine glacial erosion landscape photos.
        (a) piedmont overdeepening (ca. 100 km), Lake Geneva
        (b) glacial valley (ca. 10 km), Lauterbrunnen
        (c) mountain cirque (ca. 1 km), Chüebodengletscher

% ----------------------------------------------------------------------
\section{Methods}
% ----------------------------------------------------------------------

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Ice sheet modelling}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Erosion law}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

% ----------------------------------------------------------------------
\section{Results}
% ----------------------------------------------------------------------

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Cumulative erosion}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    Fig.~\ref{fig:cumulative} -- Cumulative erosion.

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Temporal evolution}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    Fig.~\ref{fig:evolution} -- Erosion rate snapshots or scatter plots.

% ----------------------------------------------------------------------
\section{Discussion}
% ----------------------------------------------------------------------

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Erosion uncertainties}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    Fig.~\ref{fig:uncertainty} -- Erosion uncertainties

% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -
\subsection{Sensitivity to climate}
% -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -- -

    Fig.~\ref{fig:sensitivity} -- Sensitivity to climate.

% ----------------------------------------------------------------------
\section{Conclusions}
% ----------------------------------------------------------------------

@@

%    \begin{figure}
%      \centerline{\includegraphics{alpero_cumulative}}
%      \caption{%
%          Modelled glacial erosion over the last glacial cycle.}
%      \label{fig:glerosion}
%    \end{figure}
